Analysis of Turkey's Trade with Selected Countries

### 2018-12-25 Final/PresentationFinal.Rmd
.

---
title: "Analysis of Turkey's Trade with Selected Countries"
author: "Group Fou\\*R*"
date: "Dec 26^th^, 2018"
output:
  ioslides_presentation:
    smaller: yes
    template: quarterly-report.html
    widescreen: yes
logo: channel4_logo.jpg
---

@@

## Explanation of Raw Data

- 10 countries’ trade data against Turkey from [Trademap.org](https://trademap.org/Index.aspx) as 4 seperate excel tables, Export&Import Quantity and Export&Import Values

@@

```{r, fig.align='center'}
glimpse(export_quantity_dataset)

@@

## Explanation of Raw Data

```{r, fig.align='center'}

@@

## Data Preparation | Joining Quantity, Value Data, Product Labels with 2 Digit Product Codes

@@

```{r, fig.align='center'}
glimpse(export_jTable)
```

## Data Preparation | Collating Same Type of Variables

@@

```{r, fig.align='center'}
# Export Values in $ 
ttable=export_jTableMELTED%>%group_by(Country,year)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))
#Import Values in $
vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))

@@

a<-ggplot(data=vtable, aes(x=Country, y=co_total,fill=year)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black")+
  ggtitle("Import Values")

b<-ggplot(data=ttable, aes(x=Country, y=co_total,fill=year)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Export Values")

@@

## Analysis | Year over Year Changes in Trade Values

```{r, message=FALSE, fig.align='center'}
tableExport <- export_jTableMELTED %>% 
  group_by(Country, year) %>%
  summarise(totalExpV=sum(Values,na.rm=TRUE)) %>%
  arrange(Country, year) %>%
  mutate(ExpValChng = (totalExpV - lag(totalExpV))/lag(totalExpV)*100)

@@

## Analysis | Year over Year Changes in Trade Values - Exports to Canada

```{r, fig.align='center', fig.height=5, fig.width=10}
# Canada and Russia significantly deviates. Investigate these countries in detail with traded products

@@

## Analysis | Year over Year Changes in Trade Values - Imports From Canada

```{r, fig.align='center', fig.height=5, fig.width=10}
# Import Analysis

@@

## Analysis | Year over Year Changes in Trade Values - Exports to Russia

```{r, fig.align='center', fig.height=5, fig.width=10}
summarytableRussianEx <- export_jTableMELTED %>%
  filter(Country=="Russian") %>%
  group_by(X__2, year) %>%
  summarise(ExportValue=sum(Values)) %>%
  arrange(X__2, year) %>%
  mutate(ExpPercChngYoY = (ExportValue - lag(ExportValue))/lag(ExportValue)*100) %>%
  mutate(ExpChngYoy=((ExportValue - lag(ExportValue)))) %>%
  filter(year!=2013)

@@

## Analysis | Year over Year Changes in Trade Values - Imports From Russia

```{r, fig.align='center', fig.height=4.5, fig.width=10}
summarytableRussianIm <- import_jTableMELTED %>%
  filter(Country=="Russian") %>%
  group_by(X__2, year) %>%
  summarise(ImportValue=sum(Values)) %>%
  arrange(X__2, year) %>%
  mutate(ImpPercChngYoY = (ImportValue - lag(ImportValue))/lag(ImportValue)*100) %>%
  mutate(ImpChngYoy=((ImportValue - lag(ImportValue)))) %>%
  filter(year!=2013)

@@

## Analysis | Trade Deficit by Countries and Years

```{r, fig.align='center'}
export_Product_Group <- export_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)

@@

## Analysis | Countries Effect on Trade Deficit

```{r , fig.align="center"}
#Normalized of Average Values for five years
Normalized_Values_By_Country <- Export_Import_JTable %>%
  #filter (year == 2017)%>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

@@

## Analysis | Correlation of Trade Deficit with FX Rate and BIST100 index

```{r, fig.align="center"}
fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)

@@

## K-Means Clustering | Determining Optimal Cluster

```{r, fig.align="center"}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

@@

## K-Means Clustering | Computing K-Means

```{r, fig.align="center"}

@@

## K-Means Clustering | Computing K-Means

```{r, fig.align="center"}

@@

## Conclusion

As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;

* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
* Germany and USA are the 2 top countries seen in both directions of trade.
* Generally we have fluctuated trade trend with Russia.
* Turkey's trade deficit analyisis gives the results : 
  + UK gives trade surplus for all years analysed 
  + China, Russia, Germany and USA have the most significant effect on trade deficit
  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
      + Electrical machinery, equipments and machinery, mechanical appliances
      + Mineral fuels, mineral oils and products of their distillation constitute 
      + Vehicles other than railway and mechanical and electronical machinery and equipments

## Conclusion

* As a result of clustering exported products;
  + Vehicles other than railway is the group we spent the most money
  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.

>>>>

---
title: "Analysis of Turkey's Trade with Selected Countries"
author: "Group Fou\\*R*"
date: "Dec 26^th^, 2018"
output:
  ioslides_presentation:
    smaller: yes
    template: quarterly-report.html
    widescreen: yes
logo: channel4_logo.jpg

---

@@

## Explanation of Raw Data and Data Preparation

- 10 countries’ trade data against Turkey are taken from [Trademap.org](https://trademap.org/Index.aspx) as 4 seperate excel tables, Export&Import Quantity and Export&Import Values

- Quantity and Value tables joined following the binding operation of 10 countries tables. Besides, 2 digit product code table have been joined.

- Same type of variables collated to one and "years"" melted to prevent repetition of quantity and value variables.

@@

```{r, fig.align='center', include= FALSE}
glimpse(export_quantity_dataset)

@@

```{r, fig.align='center', include=FALSE}

@@

@@

```{r, fig.align='center', fig.height=5, fig.width=4.5, include=FALSE}
glimpse(export_jTable)
```

@@

## Analysis | Breakdown of Total Export & Import

```{r, fig.align='center', fig.height=5, fig.width=5}
# Export Values in $ 
ttable=export_jTableMELTED%>%group_by(Country,year)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))
#Import Values in $
vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))

@@

a<-ggplot(data=vtable, aes(x=Country, y=co_total,fill=year)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black")+
  ggtitle("Import Values") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b<-ggplot(data=ttable, aes(x=Country, y=co_total,fill=year)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black")+ggtitle("Export Values") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, message=FALSE, fig.align='center', fig.height=5, fig.width=5}
tableExport <- export_jTableMELTED %>% 
  group_by(Country, year) %>%
  summarise(totalExpV=sum(Values,na.rm=TRUE)) %>%
  arrange(Country, year) %>%
  mutate(ExpValChng = (totalExpV - lag(totalExpV))/lag(totalExpV)*100)

@@

## Analysis | Year over Year Changes in Trade Values - Export & Import - Canada {#slide36}

<style> 
  #slide36 > p { 
    margin-top: -50px; 
  } 
</style>

```{r, fig.align='center', fig.height=5, fig.width=5}
# Canada and Russia significantly deviates. Investigate these countries in detail with traded products

@@

```{r, fig.align='center', fig.height=5, fig.width=5}
# Import Analysis

@@

## Analysis | Year over Year Changes in Trade Values - Exports & Imports to Russia {#slide37}

<style> 
  #slide37 > p { 
    margin-top: -50px; 
  } 
</style>

```{r, fig.align='center', fig.height=5, fig.width=5}
summarytableRussianEx <- export_jTableMELTED %>%
  filter(Country=="Russian") %>%
  group_by(X__2, year) %>%
  summarise(ExportValue=sum(Values)) %>%
  arrange(X__2, year) %>%
  mutate(ExpPercChngYoY = (ExportValue - lag(ExportValue))/lag(ExportValue)*100) %>%
  mutate(ExpChngYoy=((ExportValue - lag(ExportValue)))) %>%
  filter(year!=2013)

@@

```{r, fig.align='center', fig.height=4.5, fig.width=5}
summarytableRussianIm <- import_jTableMELTED %>%
  filter(Country=="Russian") %>%
  group_by(X__2, year) %>%
  summarise(ImportValue=sum(Values)) %>%
  arrange(X__2, year) %>%
  mutate(ImpPercChngYoY = (ImportValue - lag(ImportValue))/lag(ImportValue)*100) %>%
  mutate(ImpChngYoy=((ImportValue - lag(ImportValue)))) %>%
  filter(year!=2013)

@@

## Analysis | Trade Deficit and Effects of Countries on Trade Deficit

```{r, fig.align='center', fig.height=4.5, fig.width=6}
export_Product_Group <- export_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)

@@

```{r , fig.align="center", fig.height=4.5, fig.width=6}
#Normalized of Average Values for five years
Normalized_Values_By_Country <- Export_Import_JTable %>%
  #filter (year == 2017)%>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

@@

```{r, fig.align="center", include=FALSE}
fileUSD= "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/gpj18-group_four/EVDS.xlsx"
usdR <- read_excel(fileUSD, col_names=FALSE, skip=1)

@@

```{r, fig.align="center", include=FALSE}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

@@

## K-Means Clustering

```{r, fig.align="center", fig.height=5.5, fig.width=4}

@@

```{r, fig.align="center", fig.height=5.5, fig.width=5.5}

@@

## Conclusion {#slide38}

<style> 
  #slide38 > p { 
    margin-top: -50px; 
  } 
</style>

<font size="3">As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;</font>

* <font size="3">Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side.</font> 
* <font size="3">Germany and USA are the 2 top countries seen in both directions of trade.</font>
* <font size="3">Generally we have fluctuated trade trend with Russia.</font>
* <font size="3">Turkey's trade deficit analyisis gives the results :</font> 
  + <font size="2">UK gives trade surplus for all years analysed</font> 
  + <font size="2">China, Russia, Germany and USA have the most significant effect on trade deficit</font>
  + <font size="2">Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.</font>
  + <font size="2">Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :</font>
      + <font size="2">Electrical machinery, equipments and machinery, mechanical appliances</font>
      + <font size="2">Mineral fuels, mineral oils and products of their distillation constitute</font> 
      + <font size="2">Vehicles other than railway and mechanical and electronical machinery and equipments</font>
* <font size="3">As a result of clustering exported products;</font>
  + <font size="2">Vehicles other than railway is the group we spent the most money</font>
  + <font size="2">Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.</font>
